---
title: "Guidebook Geographies Exploration"
format:
   html:
     df-print: paged
editor: visual
---

## Mapping Top 25 Cities in all Guidebook Data for 1983

```{r}
library(ggplot2)
library(tidyverse)

relative.count <- read.csv("relative-data.csv")
## Generate Ranked count for data (using all of damron)
rank <- relative.count %>%  group_by(publication) %>% mutate(rank = rank(-count, ties.method = 'min'))
rank <- rank %>% filter(rank < 25)

usa <- map_data("state")
ggplot() + 
  geom_map( data = usa, map = usa, aes(long, lat, map_id=region)) + borders("state", fill = "white", colour = "grey80") +   coord_fixed(1) +
  geom_point(data = rank, mapping = aes(x=lon, y=lat, color = publication)) + facet_wrap(~publication, nrow = 2) +  theme(legend.position="bottom")

```

Print city rank in each guide.

```{r}
gg <- rank %>% filter(publication == "Gaia's Guide") %>% select(publication, city, state, count, rank) %>% arrange(rank)
gg
```

```{r}
dg <- rank %>% filter(publication == "Bob Damron's Address Book") %>% select(publication, city, state, count, rank) %>% arrange(rank)
dg
```

```{r}
lc <- rank %>% filter(publication == "Lesbian Connection") %>% select(publication, city, state, count, rank) %>% arrange(rank)
lc
```

## Mapping the Top 25 Cities for Women's Spaces in Guidebooks

The primary difference in this measurement is that we sort the Damron guides to include only spaces that he classified as "(L) for Ladies/Ms OR Lesbians, but not exclusively unless noted."

```{r}
relative.w.count <- read.csv("relative-data-womens.csv")
## Generate Ranked count for data (using all of damron)
rank.w <- relative.w.count %>%  group_by(publication) %>% mutate(rank = rank(-count, ties.method = 'min'))
rank.w <- rank.w %>% filter(rank < 25)

usa <- map_data("state")
ggplot() + 
  geom_map( data = usa, map = usa, aes(long, lat, map_id=region)) + borders("state", fill = "white", colour = "grey80") +   coord_fixed(1) +
  geom_point(data = rank.w, mapping = aes(x=lon, y=lat, color = publication)) + facet_wrap(~publication, nrow = 2) +  theme(legend.position="bottom")
```

The only dataset that is different here is the Damron dataset

```{r}
dg.w <- rank.w %>% filter(publication == "Bob Damron's Address Book") %>% select(publication, city, state, count, rank) %>% arrange(rank)
dg.w
```
